\documentclass[12pt]{article}
\usepackage[]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{blindtext}
\usepackage{flafter}
\usepackage[T1]{fontenc}
\usepackage{color,hyperref}
\usepackage[document]{ragged2e}
\thispagestyle{empty}
\geometry{paperheight=11in, paperwidth=8.5in, margin=1cm}
\newcommand{\resumename}[1]{\LARGE\textbf{#1} \hfill \small}
\newcommand{\sbullet}{\raisebox{0.35ex}{\tiny$\bullet$}\hspace*{3pt}}
\titleformat{\section}{\bfseries}{}{1em}{}[{\titlerule[0.8pt]}]
\titlespacing*{\section}{0em}{1em}{0.5em}
\titleformat{\subsection}[runin]{\normalfont\bfseries}{}{1em}{}[]
\titlespacing*{\subsection}{0em}{0.5em}{0em}

\begin{document}
\noindent
\resumename{Akanksha Bhadauria} \raggedright Email: \href{mailto:bhadauriakanksha2403@gmail.com}{bhadauriakanksha2403@gmail.com} \\
\hfill Mobile: \href{tel:+918433434933}{+91-8433434933}\\
Linkedin: \href{https://www.linkedin.com/in/bhadauriakanksha2403/}{https://www.linkedin.com/in/bhadauriakanksha2403/} \\
Codechef: \href{https://www.codechef.com/users/tanishka125}{https://www.codechef.com/users/tanishka125} \\
Codeforces: \href{https://codeforces.com/profile/tanu24}{https://codeforces.com/profile/tanu24} \\
Github: \href{https://github.com/Akanksha2403}{https://github.com/akanksha2403} \\
\section*{EDUCATION}
\subsection*{Indian Institute of Information Technology, Lucknow}      \hfill \textbf{Lucknow, Uttar Pradesh, India} \\
Bachelor of Technology - Information Technology (CGPA: 8/10) \hfill \textit{December 2020 - Present (May 2024)} \\
\subsection*{John Milton Public School}                       \hfill \textbf{Agra, Uttar Pradesh, India} \\
CBSE Class 10\textsuperscript{th} \& 12\textsuperscript{th} (10\textsuperscript{th} Percentage : 94\%, 12\textsuperscript{th} Percentage : 95.6\%) \hfill \textit{December 2016 - June 2020} \\ 

\section*{PROJECTS}
\subsection*{\href{https://akanksha2403.pythonanywhere.com/}{ShopApp}}~ Django $\vert$ HTML $\vert$ CSS3 $\vert$ JavaScript $\vert$ Bootstrap\hfill \textit{August 2021 - September 2021} \\ 
\begin{itemize}[topsep=0pt,itemsep=1pt,partopsep=1pt, parsep=1pt]
    \item A full dummy shop app for buying items. 
    \item Served login authentication using Django auth
    \item Used Bootstrap Framework along with CSS3 and JavaScript for front-end, making website more interactive.
    \item Used Django (Python) as back-end framework. 
    \item Implemented Django-admin for storing ID and password for each user. 
\end{itemize}
\subsection*{Machine Learning Datasets}~ Python $\vert$ Pandas $\vert$ Scikit-Learn $\vert$ Matplotlib $\vert$ Seaborn\hfill \textit{May 2021 - July 2021} \\
\begin{itemize}[topsep=0pt,itemsep=1pt,partopsep=1pt, parsep=1pt]
    \item Cleaned raw Datasets and stored in tabular form using \textbf{Numpy} and \textbf{Pandas} libraries.
    \item Converted data to human-readable chart representation using libraries like \textbf{Matplotlib} and \textbf{Seaborn}.
    \item Prediction models are trained and tested for accuracy using \textbf{Scikit-Learn}.
\end{itemize}

\subsection*{\href{https://github.com/prabhavagrawal7/grievance-addressal-system}{Grievance Addressal System}}~ Django $\vert$ Data Structures $\vert$ CSS $\vert$ JS $\vert$ BootStrap \hfill \textit{April 2021 - May 2021} \\
\begin{itemize}[topsep=0pt,itemsep=1pt,partopsep=1pt, parsep=1pt]
    \item Complaints or reports lodged by staff can be addressed and followed up on through this website.
	\item In the event that the complaint is not handled after a predetermined amount of time, it is automatically escalated to its next senior authority.
	\item If senior authority fails to respond the complaint, the complaint will be further escalated until it is solved. 
\end{itemize}
\section*{ACHIEVEMENTS}
\begin{itemize}[leftmargin=*, topsep=0pt,itemsep=2pt,partopsep=2pt, parsep=2pt]
\item {\textbf{Reached finals in HackOFiesta v2.0} Equinox 2021 conducted by IIITL}
\item \textbf{Specialist} at \textbf{Codeforces} (Max rated: \textbf{1417})
\item \textbf{4 star} at \textbf{CodeChef} (Max rated: \textbf{1909})
\item Global rank \textbf{32} in \href{https://www.codechef.com/rankings/START64B?search=tanishka125}{\textbf{CodeChef Starters 64 (Div. 2)}}
\item Global rank \textbf{78} in \href{https://www.codechef.com/rankings/START19C?search=tanishka125}{\textbf{CodeChef Starters 19 (Div. 3)}}
\item Global rank \textbf{212} in \href{https://www.codechef.com/rankings/START62B?search=tanishka125}{\textbf{Codechef starters 62 (Div. 2)}}
\item Global rank \textbf{1400} in \href{https://codeforces.com/contest/1686/standings/participant/133609891#p133609891}{\textbf{Codeforces Round 794 (Div. 2)}}
\item Global rank \textbf{1889} in \href{https://codeforces.com/contest/1749/standings/participant/142527940#p142527940}{\textbf{Educational Codeforces Round 138 (Div. 2)}}
\item Global rank \textbf{2274} in \href{https://codeforces.com/contest/1750/standings/participant/143608695#p143608695}{\textbf{CodeTON Round 3 (Div. 1 + Div. 2)}} 
\item Global rank \textbf{2467} in \href{https://codingcompetitions.withgoogle.com/kickstart/submissions/00000000008cb409/0000000000648019} {\textbf{Google Kickstart 2022 Round F}}

\end{itemize}
\section*{TECHNICAL SKILLS}
\subsection*{Languages}               \hspace*{4.4cm} C/C++ \sbullet Python \\
\subsection*{Frameworks \& Libraries} \hspace*{1.74cm} Django \sbullet NumPy \sbullet Pandas \sbullet Scikit-learn \sbullet Bootstrap \sbullet Matplotlib \sbullet Seaborn\\
\subsection*{Dev Tools}               \hspace*{4.45cm} Git/GitHub \sbullet VS Code \sbullet Jupyter Notebook \\ 
\subsection*{Academic Coursework}     \hspace*{2.10cm} Data Structures and Algorithms \sbullet OOPS \sbullet DBMS \\

\end{document}