\documentclass[letterpaper, 10pt, oneside]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{array}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{enumitem}
\usepackage{calc}
\usepackage{lipsum}
\usepackage{soul}

\definecolor{lightgray}{RGB}{245, 245, 245}
\definecolor{darkgray}{RGB}{112, 112, 112}
\definecolor{blue}{RGB}{66, 133, 244}
\definecolor{orange}{RGB}{255, 152, 0}
\definecolor{green}{RGB}{106, 170, 116}
\definecolor{purple}{RGB}{156, 108, 176}

\newcommand{\uline}[1]{\textcolor{blue}{\underline{\smash{#1}}}}

\begin{document}
\thispagestyle{empty}

\noindent
{\Large\bfseries Prabhav Agrawal}

\vspace{0.2cm}
\noindent
\textcolor{darkgray}{\rule{\textwidth}{0.4pt}}

\vspace{0.2cm}
\noindent
\textcolor{blue}{\textbf{Email:}} \textcolor{black}{prabhavagra7@gmail.com}
\hspace{1.8cm} \textcolor{blue}{\textbf{Mobile:}} \textcolor{black}{+91-9653051636}

\vspace{0.2cm}
\noindent
\textcolor{blue}{\textbf{LinkedIn:}} \textcolor{black}{\href{https://www.linkedin.com/in/prabhavagra7/}{linkedin.com/in/prabhavagra7}}
\hspace{0.8cm} \textcolor{blue}{\textbf{GitHub:}} \textcolor{black}{\href{https://github.com/prabhavagra7}{github.com/prabhavagra7}}
\hspace{0.8cm} \textcolor{blue}{\textbf{Codeforces:}} \textcolor{black}{\href{https://codeforces.com/profile/prabhavagra7}{codeforces.com/users/prabhavagra7}}

\vspace{0.2cm}
\noindent
\textcolor{darkgray}{\rule{\textwidth}{0.4pt}}

\vspace{0.5cm}
\noindent
{\Large\bfseries EDUCATION}

\vspace{0.2cm}
\noindent
\textcolor{blue}{\textbf{Indian Institute of Information Technology, Lucknow}} \hspace{3.8cm} \textcolor{darkgray}{December 2020 - Present (May 2024)}
\textcolor{black}{Bachelor of Technology - Information Technology (CGPA: 7.89/10)}

\vspace{0.2cm}
\noindent
\textcolor{blue}{\textbf{Sunbeam English School}} \hspace{7.4cm} \textcolor{darkgray}{December 2009 - Present (May 2024)}
\textcolor{black}{CBSE Class 10th \& 12th (CGPA: 9.4, 12th Percentage: 89.6\%)}

\vspace{0.2cm}
\noindent
\textcolor{darkgray}{\rule{\textwidth}{0.4pt}}

\vspace{0.5cm}
\noindent
{\Large\bfseries EXPERIENCE}

\vspace{0.2cm}
\noindent
\textcolor{blue}{\textbf{Microsoft}} \hspace{9.3cm} \textcolor{darkgray}{May 2023 - July 2023}
\textcolor{black}{Software Engineering (Intern)}
\begin{itemize}
 \item Designed a two-stage process to accurately filter context in real-time text streaming using local processing, reducing load on large language models (LLMs).
 \item Explored the UI/UX to seamlessly accommodate new features, maintaining a user-centric design approach.
 \item Utilized Semantic Search to evaluate the relationship between detected \& desired context, enabling context identification.
 \item Enhanced the UI/UX of TypeScript/TensorFlow.js
\end{itemize}

\vspace{0.2cm}
\noindent
\textcolor{blue}{\textbf{Watchow}} \hspace{10.2cm} \textcolor{darkgray}{April 2022 - May 2023}
\textcolor{black}{Django | Scikit-learn | NumPy | Pandas | Matplotlib | jQuery | JavaScript}
\begin{itemize}
 \item Applied content-based recommendation system in the project.
 \item Improved UI/UX with personalized recommendation, search bar, movie pages, and user authentication.
 \item Created a dummy website for shopping books using Django, HTML, CSS, JavaScript, and Bootstrap.
 \item Implemented user authentication and cart checkout functionality.
 \item Developed an order tracking page to help users keep track of their orders.
 \item Deployed a web-based Complaint Management System, optimizing complaint handling.
 \item Managed a database schema to ensure secure access to the system.
 \item Implemented email escalation to higher authorities based on response deadlines, enhancing workflow efficiency and ensuring minimal response delays.
 \item Automated compliance with a tree structure, utilizing self-defined roles for efficient designation hierarchy management.
 \item Rated "Expert" on Codeforces (Max Rated: 1809)
 \item Rated 5 star on CodeChef (Max Rated: 2031)
 \item Global rank 7 in CodeChef Starters 64 (Div. 2)
 \item Global rank 34 in CodeChef Starters 32 (Div. 2)
 \item Global rank 175 out of 10k in Codeforces Round 857 (Div. 2)
 \item Global rank 320 out of 10k in Codeforces Round 868 (Div. 2)
\end{itemize}

\vspace{0.2cm}
\noindent
\textcolor{darkgray}{\rule{\textwidth}{0.4pt}}

\vspace{0.5cm}
\noindent
{\Large\bfseries ACHIEVEMENTS}

\vspace{0.2cm}
\noindent
\textcolor{blue}{\textbf{Senior Member, Competitive Programming Wing, Axios}} \hspace{1.8cm} \textcolor{darkgray}{May 2022 - Aug 2023}
\textcolor{black}{Indian Institute of Information Technology, Lucknow}

\vspace{0.2cm}
\noindent
\textcolor{darkgray}{\rule{\textwidth}{0.4pt}}

\vspace{0.5cm}
\noindent
{\Large\bfseries TECHNICAL SKILLS}

\vspace{0.2cm}
\noindent
\textcolor{blue}{\textbf{Programming Languages}} \hspace{4.8cm} \textcolor{black}{C++, Python, HTML, CSS, JavaScript, Matlab, Seaborn, Bootstrap, jQuery}
\textcolor{blue}{\textbf{Frameworks \& Libraries}} \hspace{4.2cm} \textcolor{black}{Django, Scikit-learn, Matplotlib, NumPy, Pandas}
\textcolor{blue}{\textbf{Tools}} \hspace{9.1cm} \textcolor{black}{Git, VS Code, Jupyter Notebook}
\textcolor{blue}{\textbf{Academic Coursework}} \hspace{4.5cm} \textcolor{black}{DSA, OOPS, DBMS, Operating System}

\vspace{0.2cm}
\noindent
\textcolor{darkgray}{\rule{\textwidth}{0.4pt}}

\end{document}
