% !TEX program = lualatex
\documentclass[12pt]{article}
\usepackage[]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{color, hyperref, xcolor}
\usepackage[document]{ragged2e}
\usepackage{fontspec}
\usepackage{xtab}
\thispagestyle{empty}
\geometry{paperheight=11.5in, paperwidth=8.5in, margin=0.8cm}
\newcommand{\resumename}[1]{\LARGE\textbf{#1} \hfill \small}
\titleformat{\section} 
  {\normalfont\fontsize{12pt}{10}\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]
\titlespacing*{\section}{0em}{0.9em}{0.5em}
\titleformat{\subsection}[runin]{\bfseries}{}{}{}[]
\titlespacing*{\subsection}{0em}{0.5em}{0em}
\begin{document}
\noindent
\resumename{Akanksha Bhadauria} 
\begin{table}[h]
	\centering
	\begin{tabularx}{\textwidth}{@{}llXr}
		Linkedin & \href{https://www.linkedin.com/in/bhadauriakanksha2403/}{linkedin.com/in/bhadauriakanksha2403/} &   & Email: \href{mailto:bhadauriakanksha2403@gmail.com}{bhadauriakanksha2403@gmail.com} \\ 
		Codechef & \href{https://www.codechef.com/users/tanishka125}{codechef.com/users/tanishka125}               &   & Mobile: \href{tel:+918433434933}{+91-8433434933}                                    \\
		Codeforces &\href{https://codeforces.com/profile/tanu24}{codeforces.com/profile/tanu24} \\
		Github &\href{https://github.com/akanksha2403}{github.com/akanksha2403} \\
	\end{tabularx}
\end{table}
\vspace{-\topsep}
\section*{EDUCATION}
\subsection*{Indian Institute of Information Technology, Lucknow}      \hfill \textbf{Lucknow, Uttar Pradesh, India} \\
Bachelor of Technology - Information Technology (CGPA: 8/10) \hfill \textit{December 2020 - Present (May 2024)} \\
\subsection*{John Milton Public School}                       \hfill \textbf{Agra, Uttar Pradesh, India} \\
CBSE Class 10\textsuperscript{th} \& 12\textsuperscript{th} (10\textsuperscript{th} Percentage : 94\%, 12\textsuperscript{th} Percentage : 95.6\%) \hfill \textit{December 2016 - June 2020} \\ 

\section*{PROJECTS}
\subsection*{\href{https://akanksha2403.pythonanywhere.com/}{ShopApp}}~ Django $\vert$ HTML $\vert$ CSS3 $\vert$ JavaScript $\vert$ Bootstrap\hfill \textit{August 2021 - September 2021} \\ 
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=1pt,partopsep=1pt, parsep=1pt]
	\item Developed a full dummy shop app that allows users to browse and purchase items online, similar to Amazon.
	\item Implemented user authentication and authorization using Django's built-in authentication system, and implemented a database to store information about products, orders, and users.
	\item Enhanced the user experience by integrating a payment gateway (Paytm) and using lazy loading to optimize performance, and added interactive elements and animations using JavaScript.
\end{itemize}
\subsection*{Machine Learning Datasets}~ Python $\vert$ Pandas $\vert$ Scikit-Learn $\vert$ Matplotlib $\vert$ Seaborn\hfill \textit{May 2021 - July 2021} \\
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=1pt,partopsep=1pt, parsep=1pt]
	\item Developed a machine learning project using Python, Pandas, Scikit-Learn, Matplotlib, and Seaborn.
	\item Applied techniques like regression and classification to explore and analyze the data, and experimented with using neural networks to make predictions or classify data.
	\item Cleaned raw datasets and stored them in a tabular form using Numpy and Pandas, and created visualizations of the data using Matplotlib and Seaborn.
\end{itemize}

\subsection*{\href{https://github.com/prabhavagrawal7/grievance-addressal-system}{Grievance Addressal System}}~ Django $\vert$ Data Structures $\vert$ CSS $\vert$ JavaScript $\vert$ Bootstrap \hfill \textit{April 2021 - May 2021} \\
\begin{itemize}[leftmargin=*,topsep=0pt,itemsep=1pt,partopsep=1pt, parsep=1pt]
	\item Developed a grievance redressal system website using Django, Data Structures (including trees), CSS, JavaScript, and Bootstrap to handle and track complaints or reports lodged by staff
	\item Implemented a smart system for addressing and escalating complaints using a tree data structure, with automatic escalation if not resolved in a predetermined time
	\item Added a user login system for users to track the status of their complaints and receive updates
\end{itemize}
\section*{ACHIEVEMENTS}
\begin{itemize}[leftmargin=*, topsep=0pt,itemsep=2pt,partopsep=2pt, parsep=2pt]
	\item {\textbf{Reached finals in HackOFiesta v2.0} Equinox 2021 conducted by IIIT Lucknow}
	\item \textbf{Specialist} at \textbf{Codeforces} (Max rated: \textbf{1417})
	\item \textbf{4 star} at \textbf{CodeChef} (Max rated: \textbf{1909})
	\item Global rank \textbf{32} in \href{https://www.codechef.com/rankings/START64B?search=tanishka125}{\textbf{CodeChef Starters 64 (Div. 2)}}
	\item Global rank \textbf{78} in \href{https://www.codechef.com/rankings/START19C?search=tanishka125}{\textbf{CodeChef Starters 19 (Div. 3)}}
	\item Global rank \textbf{207} in \href{https://www.codechef.com/rankings/START62B?search=tanishka125}{\textbf{CodeChef Starters 62 (Div. 2)}}
	\item Global rank \textbf{1077} in \href{https://codeforces.com/contest/1771/standings/participant/145587929#p145587929}{\textbf{Codeforces Round 837 (Div. 2)}}
	\item Global rank \textbf{1400} in \href{https://codeforces.com/contest/1686/standings/participant/133609891#p133609891}{\textbf{Codeforces Round 794 (Div. 2)}}
	\item Global rank \textbf{1695} in \href{https://codeforces.com/contest/1772/standings/participant/146151939#p146151939}{\textbf{Codeforces Round 839 (Div. 3)}}
	\item Global rank \textbf{1889} in \href{https://codeforces.com/contest/1749/standings/2/participant/142527940#p142527940}{\textbf{Educational Codeforces Round 138 (Rated for Div. 2)}} 
	\item Global rank \textbf{2467} in \href{https://codingcompetitions.withgoogle.com/kickstart/submissions/00000000008cb409/0000000000648019} {\textbf{Google Kickstart 2022 Round F}}
\end{itemize}
\begin{table}[h]
	\section*{TECHNICAL SKILLS}
	\vspace{-2pt}
	\centering
	\begin{tabularx}{\textwidth}{@{}ll}
		\textbf{Languages} & C/C++, Python                                                       \\
		\textbf{Frameworks \& Libraries} & Django, NumPy, Pandas, Scikit-learn, Bootstrap, Matplotlib, Seaborn \\
		\textbf{Dev Tools} & Git/GitHub, VS Code, Jupyter Notebook                               \\ 
		\textbf{Academic Coursework} & Data Structures and Algorithms, OOPS, DBMS                          \\
	\end{tabularx}
\end{table}

\end{document}