\documentclass[a4paper,10pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}

\begin{document}

\begin{letter}{Hiring Manager \\ Optiver \\ Company Address}
\opening{Dear Hiring Manager,}

I am writing to express my strong interest in the Graduate Software Engineer position at Optiver, as advertised. With a background in Information Technology and a passion for problem-solving, I am excited about the opportunity to contribute to Optiver's mission of leveraging technology to enhance liquidity, pricing accuracy, transparency, and market stability in the financial markets.

Here's how my qualifications align with the requirements and expectations for this role:

\begin{itemize}[leftmargin=*]
\item \textbf{Education:} \\
I hold a Bachelor of Technology in Information Technology from the Indian Institute of Information Technology Lucknow, with a commendable CGPA of 7.89/10. My academic background has provided me with a solid foundation in computer science principles, which I believe is essential for excelling in this role.

\item \textbf{Experience:} \\
During my internship at Microsoft as a Software Development Engineer (SDE), I had the privilege of working on projects that demanded innovation and technical acumen. I designed a two-stage process to filter context in real-time text streams, reducing the load on large language models. I also utilized semantic searching to enhance context identification. Moreover, I improved the UI/UX for seamless feature integration, emphasizing a user-centric design approach. My experience with React, TypeScript, and TensorFlow.js aligns well with the technologies used at Optiver.

\item \textbf{Projects:} \\
I have hands-on experience with web development using Django, HTML, CSS, and JavaScript, as demonstrated by my projects such as "Watchnow" and "Bookshop." These projects showcase my ability to develop user-friendly interfaces and implement personalized features. Additionally, my work on the "Grievance Addressal System" involved optimizing complaint handling, database management, and complaint escalation, all of which are relevant skills for this role.

\item \textbf{Achievements:} \\
I take pride in my achievements as a competitive programmer, with ratings of Expert on Codeforces (Max Rated: 1809) and 5-star on Codechef (Max Rated: 2031). My participation in Microsoft Engage and Amazon ML Summer School programs reflects my dedication to continuous learning and growth in the tech industry. These experiences have honed my problem-solving skills and ability to work in dynamic environments.

\item \textbf{Position of Responsibility:} \\
As a Senior Member of the Competitive Programming Wing at my institute, I have gained valuable teamwork and leadership skills. This position has allowed me to collaborate effectively with peers and contribute to the growth of the programming community.

\item \textbf{Technical Skills:} \\
I am proficient in languages such as C++, Python, HTML, and CSS. Additionally, I have experience with Django, Scikit-learn, Matplotlib, Bootstrap, and other relevant frameworks and libraries. My familiarity with Git, VS Code, and Jupyter Notebook ensures efficient development and collaboration.
\end{itemize}

I am excited about the prospect of joining Optiver and contributing to its mission-critical work. My passion for technology, problem-solving abilities, and commitment to continuous improvement align perfectly with the qualities sought in a Graduate Software Engineer. I look forward to the opportunity to discuss how my skills and experiences can contribute to the success of Optiver.

Thank you for considering my application. I am available at your earliest convenience for an interview. You can reach me at prabhavagrawal7@gmail.com or by phone at +91-9653051636.

\closing{Sincerely, \\
Prabhav Agrawal}
\end{letter}

\end{document}
