\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{color, hyperref, xcolor}
\usepackage[document]{ragged2e}
\usepackage{xtab}
\usepackage{graphicx}
\usepackage{multirow}
\geometry{paperheight=11in, paperwidth=8.5in, margin=1cm}
\thispagestyle{empty}

\newcommand{\resumename}[1]{\LARGE\textbf{#1} \hfill \small}

\titleformat{\section}
  {\normalfont\fontsize{12pt}{14pt}\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

\titlespacing*{\section}{0em}{0.5em}{0.5em}
\titleformat{\subsection}[runin]{\bfseries}{}{}{}[]
\titlespacing*{\subsection}{0em}{0.5em}{0em}

\begin{document}
\noindent
\resumename{Akanksha Bhadauria}

\vspace*{-6pt}
\begin{table}[h]
	\hspace*{-10px}
\begin{tabular}{llr}
	\textbf{Linkedin} & \href{https://linkedin.com/in/bhadauriakanksha2403}{linkedin.com/in/bhadauriakanksha2403} \hspace*{4cm}&  Email: \href{mailto:lit2020026@iiitl.ac.in}{lit2020026@iiitl.ac.in} \\
	\textbf{Github} & \href{https://github.com/akanksha2403}{github.com/akanksha2403} & Mobile: \href{tel:+918433434933}{+91 8433434933}\\
	\textbf{Codeforces} & \href{https://codeforces.com/profile/tanu24}{codeforces.com/profile/tanu24} & \\
	\textbf{Codechef} & \href{https://codechef.com/users/tanishka125}{codechef.com/users/tanishka125} & \\
\end{tabular}
\end{table}

\vspace{-\topsep}
\section*{EDUCATION}
\subsection*{Indian Institute of Information Technology, Lucknow} \hfill \textbf{Lucknow, Uttar Pradesh, India} \\
Bachelor of Technology - Information Technology (CGPA: 7.72/10) \hfill \textit{December 2020 - Present (May 2024)} \\
\subsection*{John Milton Public School} \hfill \textbf{Agra, Uttar Pradesh, India} \\
CBSE Class 10\textsuperscript{th} \& 12\textsuperscript{th} (10\textsuperscript{th} Percentage: 94\%, 12\textsuperscript{th} Percentage: 95.6\%) \hfill \textit{December 2016 - June 2020}

\section*{PROJECTS}
\subsection*{\href{https://akanksha2403.pythonanywhere.com/}{ShopApp}}~ Django $\vert$ HTML $\vert$ CSS $\vert$ JavaScript $\vert$ Bootstrap \\
\begin{itemize}[leftmargin=20px, topsep=0.5pt, itemsep=1.5pt, partopsep=0.5pt, parsep=0.5pt]
  \item Developed a dummy shop app that allows users to browse and purchase items online, similar to Amazon.
  \item Users can buy, add to cart, or track orders on the website.
  \item Implemented a database to store information about products, orders, and users.
\end{itemize}
\subsection*{Machine Learning Datasets}~ Python $\vert$ Pandas $\vert$ Scikit-Learn $\vert$ Matplotlib $\vert$ Seaborn \\
\begin{itemize}[leftmargin=20px, topsep=0.5pt, itemsep=1.5pt, partopsep=0.5pt, parsep=0.5pt]
  \item This collection of projects explored various machine learning models and techniques on different datasets to gain hands-on experience in Machine Learning.
  \item Raw datasets were cleaned using NumPy and Pandas, and meaningful visualizations of the data were created using Matplotlib and Seaborn.
  \item Data was preprocessed and prepared for machine learning models using Scikit-Learn.
\end{itemize}

\subsection*{\href{https://github.com/Akanksha2403/no_issues}{No Issues}}~ Django $\vert$ CSS $\vert$ JavaScript $\vert$ Bootstrap $\vert$ Perspective API \\
\begin{itemize}[leftmargin=20px, topsep=1pt, itemsep=1.5pt, partopsep=1pt, parsep=1pt]
	\item Developed a web-based Complaint Management System, optimizing complaint handling.
	\item Designed a database schema with a tree structure, utilizing self-referential foreign keys for efficient designation hierarchy management.
  \item Implemented user authentication to ensure secure access to the system.
  \item Automated complaint escalation to higher authorities based on response deadlines, enhancing workflow efficiency and ensuring timely resolution.
  \item Employed offensive content detection mechanisms to maintain a respectful online environment.
\end{itemize}


\section*{ACHIEVEMENTS}
\begin{itemize}[leftmargin=15px, topsep=1pt, itemsep=1pt, partopsep=2pt, parsep=2pt]
  \item \textbf{Reached finals in HackOFiesta v2.0} Equinox 2021 conducted by IIIT Lucknow.
  \item \textbf{Specialist} at \textbf{Codeforces} (Max rated: \textbf{1520}).
  \item \textbf{4 star} at \textbf{CodeChef} (Max rated: \textbf{1987}).
  \item Global rank \textbf{32} in \href{https://www.codechef.com/rankings/START64B?search=tanishka125}{\textbf{CodeChef Starters 64 (Div. 2)}}.
  \item Global rank \textbf{78} in \href{https://www.codechef.com/rankings/START19C?search=tanishka125}{\textbf{CodeChef Starters 19 (Div. 3)}}.
  \item Global rank \textbf{207} in \href{https://www.codechef.com/rankings/START62B?search=tanishka125}{\textbf{CodeChef Starters 62 (Div. 2)}}.
  \item Global rank \textbf{386} in \href{https://codeforces.com/contest/1833/standings/participant/155663820#p155663820}{\textbf{Codeforces Round 874 (Div. 3)}}.
  \item Global rank \textbf{772} in \href{https://codeforces.com/contest/1816/standings/participant/153504271#p153504271}{\textbf{Codeforces Round 865 (Div. 2)}}.
  \item Global rank \textbf{928} in \href{https://codeforces.com/contest/1798/standings/participant/152498821#p152498821}{\textbf{Codeforces Round 860 (Div. 2)}}.
  \item Global rank \textbf{2467} in \href{https://codingcompetitions.withgoogle.com/kickstart/submissions/00000000008cb409/0000000000648019}{\textbf{Google Kickstart 2022 Round F}}.
\end{itemize}

\section*{TECHNICAL SKILLS}
\vspace{-2pt}
\begin{tabularx}{\textwidth}{@{}ll}
  \textbf{Languages} & C/C++, Python, Shell \\
  \textbf{Frameworks \& Libraries} & Django, NumPy, Pandas, Scikit-learn, Bootstrap, Matplotlib, Seaborn \\
  \textbf{Dev Tools} & Git/GitHub, VS Code, Jupyter Notebook \\
  \textbf{Academic Coursework} & DSA, Operating System, OOPS, DBMS, Computer Networks \\
\end{tabularx}

\end{document}
