\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\setlist[itemize]{label={-}}
\usepackage{tabularx}
\usepackage{color, hyperref, xcolor}
\usepackage[document]{ragged2e}
\usepackage{graphicx}
\usepackage{multirow}
\input{glyphtounicode}
\pdfgentounicode=1
\definecolor{linkcolor}{HTML}{003c51}
\hypersetup{
	colorlinks=true, 
	urlcolor=linkcolor
} 
\hyphenpenalty=10000
\exhyphenpenalty=10000
\sloppy
\thispagestyle{empty}
\geometry{paperheight=11in, paperwidth=8.5in, top=0.8cm, bottom=1cm, left=1cm, right=1cm}
\setlength{\emergencystretch}{1em}
\titleformat{\section} 
  {\normalfont\fontsize{10pt}{9pt}\bfseries}{}{0.5em}{}[{\titlerule[0.1pt]}]
\titlespacing*{\section}{0em}{0.65em}{0.4em}
\titleformat{\subsection}[runin]{\bfseries}{}{}{}[]
\titlespacing*{\subsection}{0em}{0.5em}{0em}

\begin{document}
{\LARGE\textbf{Prabhav Agrawal}} \\
\vspace*{6pt}

\noindent
{\small
\begin{minipage}[t]{0.64\textwidth}
\textbf{GitHub:} \href{https://github.com/prabhavagrawal7}{\nolinkurl{github.com/prabhavagrawal7}}\\
\textbf{LinkedIn:} \href{https://linkedin.com/in/prabhavagrawal7}{\nolinkurl{linkedin.com/in/prabhavagrawal7}}\\
\textbf{Codeforces:} \href{https://codeforces.com/profile/prabhavagrawal7}{\nolinkurl{codeforces.com/profile/prabhavagrawal7}}
\end{minipage}\hfill
\begin{minipage}[t]{0.34\textwidth}
\raggedleft
\textbf{Email:} \href{mailto:prabhavagrawal7@gmail.com}{\nolinkurl{prabhavagrawal7@gmail.com}}\\
\textbf{Phone:} +91-9653051636
\end{minipage}
}
	
\section*{EDUCATION}
\subsection*{Indian Institute of Information Technology Lucknow}	\hfill\textbf{Lucknow, Uttar Pradesh, India} \\
Bachelor of Technology - Information Technology 	\hfill\textit{Dec 2020 -  Jul 2024} \\

\section*{EXPERIENCE}
\textbf{Microsoft} \hfill \textbf{Noida, Uttar Pradesh, India} \\
Software Engineer  \hfill \textit{July 2024 - Present} \\
\begin{itemize}[topsep=1pt, itemsep=1.2pt, partopsep=1pt, parsep=1pt]
	\item Shipped Copilot chat pane upgrades for Word/PowerPoint on iOS: upgraded service integration and enabled multimodal workflows (e.g., image generation, code execution); partnered with cross-functional teams to validate rollout configurations.
	\item Built LLM evaluation infrastructure for Word/PowerPoint agent comprehension workflow: prompt/system tuning, debugging document retrieval and search grounding flows, and added LLM-driven report generation.
	\item Enabled grounding for local/non-cloud attachments by seeding offline document context; coordinated with service and client teams to ensure correct context seeding.
	\item Implemented enterprise admin controls for multi-account scenarios; improved disabled-user UX (e.g., removed in-document nudges) and ensured compliance by disabling prefetch for Copilot-disabled enterprise users.
	\item Enforced file upload policy for Copilot chat pane (Word/PPT iOS); uncovered a spec gap around grounding when uploads are restricted and drove a cross-team fix.
	\item Enabled SafeLink for App Chat iOS (Word/PPT): facilitated cross-team design, fixed citation URL/link embedding issues, and helped align service vs. client responsibilities.
	\item Improved telemetry quality and segmentation: fixed PLT/UPLT (Perceived Latency) data gathering issues, enabled structured logging for iOS with dashboard support, restored performance metric accuracy via entry-point instrumentation fixes, and added document tenant ID for usage segmentation.
	\item Improved reliability and dev velocity: automated local deployment/testing to speed up iteration, improved audio summary caching, strengthened accessibility (VoiceOver), resolved release regressions via dependency coordination, and supported on-call rotations.
\end{itemize}


\textbf{Rubrik} \hfill \textbf{Bengaluru, Karnataka, India} \\
Software Engineer Intern  \hfill \textit{Jan 2024 - Jun 2024} \\
\begin{itemize}[topsep=1pt, itemsep=1.2pt, partopsep=1pt, parsep=1pt]
	\item Built Luna (Offline Recovery) workflows in React/TypeScript with Apollo (GraphQL), and authored comprehensive manual test plans to accelerate delivery.
	\item Improved core table component UX by fixing lazy loading, refetching, and mutation-driven query updates.
	\item Shipped archival location setup for Rubrik Cloud Vault; enabled concurrent mode, fixed flaky tests, and performed integration testing.
\end{itemize}



\textbf{\href{https://drive.google.com/file/d/1AmHyhbctI577QKw8zxRCBjzVVyGyQHvb/view}{Microsoft}} \hfill \textbf{Noida, Uttar Pradesh, India} \\
Software Engineer Intern  \hfill \textit{May 2023 - Jul 2023} \\
\begin{itemize}[topsep=1pt, itemsep=1.2pt, partopsep=1pt, parsep=1pt]
	\item Integrated speech-to-text voice input into the Copilot pane for Office web apps (React/TypeScript).
	\item Designed and built a two-stage streaming filter to process real-time text input and reduce GPT-4 usage.
	\item Evaluated intent-detection and text segmentation approaches (punctuation-based to RNNs), balancing filtering efficiency vs. output quality.
\end{itemize}

\section*{ACHIEVEMENTS}
\begin{itemize}[leftmargin=20pt, topsep=0.5pt, itemsep=0.5pt, partopsep=0.5pt, parsep=0.5pt]
    \item Rated \textbf{Expert (1809)} on \href{https://codeforces.com/profile/prabhavagrawal7}{Codeforces}
    \item Secured AIR \textbf{1} and Global Rank \textbf{7} in \href{https://www.codechef.com/rankings/START64B?filterBy=Country%3DIndia&itemsPerPage=100}{CodeChef Starters 64 (Div.2)}
    \item Secured Global Rank \textbf{175/14,000+} in \href{https://codeforces.com/contest/1853/standings/participant/159682595#p159682595}{Codeforces Round 887 (Div.2)}
\end{itemize}


\section*{TECHNICAL SKILLS}
{\small
\noindent
\textbf{Languages:} C++, Python, TypeScript, Swift, Objective-C\\
\textbf{Frameworks \& Libraries:} React, GraphQL (Apollo), Django, Swift UI, ML (scikit-learn)\\
\textbf{Core CS:} Data Structures and Algorithms, OOPS, DBMS, Operating System, Problem Solving
}
\end{document}
