\documentclass{letter}
\usepackage[a4paper, margin=2cm]{geometry}
\usepackage{hyperref}

\signature{Prabhav Agrawal}

\begin{document}

\begin{letter}{\textbf{Rubrik}\\
Software Engineering Winter Internship\\
Bangalore, India Office}

\opening{Dear Hiring Team,}

I am writing to express my strong interest in the Software Engineering Winter Internship at Rubrik. With a solid background in Information Technology and a passion for data protection and management, I believe I would be a valuable addition to your esteemed organization.

\textbf{Background:}
My name is Prabhav Agrawal, and I recently completed my Bachelor of Technology in Information Technology from the Indian Institute of Information Technology, Lucknow, where I achieved an CGPA of 8.11/10. Additionally, I excelled in my CBSE Class 10th and 12th exams at Sunbeam English School, with a remarkable 9.4 CGPA in 10th and 89.6 in 12th class.

\textbf{Experience:}
During my time as an SDE Intern at Microsoft, I had the opportunity to work extensively with TypeScript, React, and NLP. Over the course of two months, I gained valuable hands-on experience in software development and honed my technical skills.

\textbf{Achievements:}
I take great pride in my achievements in the competitive programming domain. As a \textbf{5 star} in Codechef and \textbf{Expert} on Codeforces, I have consistently ranked among the top participants in various coding contests. I have ranked under 500 rank in 7+ contests and under 1000 rank in 23+ contests in Codeforces. 

\textbf{Conclusion:}
I am confident that my technical problem-solving abilities and strong work ethic make me an ideal candidate for the Software Engineering Winter Internship at Rubrik. Given the opportunity, I am eager to learn from your talented team, contribute to Rubrik's success, and develop myself as a professional in the field of data security and cloud management.

Thank you for considering my application. I am excited about the prospect of joining Rubrik and contributing to its success. Please find my resume attached for your review. I look forward to the possibility of discussing my qualifications in more detail during an interview.

\closing{Sincerely,}

\encl{Resume}

\end{letter}
\end{document}
